---
title: "B3"
author: "Jeremiah Theisen"
date: "2024-08-27"
output: pdf_document
---

```{r hsb2_download}
hsb2 = read.csv("https://github.com/TienChih/tbil-stats/raw/main/data/hsb2.csv")
names(hsb2)
```

## Activity 1.3.1

```{r hsb2_plot1}
plot(hsb2$read, hsb2$math, xlab="Reading Score ", ylab="Math Score ", pch=10)
```

a.  Each dot represents one student. Its coordinates represent the student's reading and math score.

b.  There is a strong positive relationship.

c.  done

d.  

```{r hsb2_plot2}
plot(hsb2$read, hsb2$write, xlab="Reading Score ", ylab="Writing Score ", pch=10)
```

e.  Each dot is a student. Its coordinates represent the student's Reading and Writing scores.

f.  There is a positive relationship, although not as strong as I was expecting

## Activity 1.3.2

```{r hsb2_histogram}
hist(hsb2$science, xlab="Science Scores", main="Distribution of Science Scores" )

```

a.  The x value represents different science score, the height represents the proportion of students which got that score.

b.  The graph looks like a triangle, but with more on the right side, after 50, than before 50. 45 and 50 are spikes, which are more frequent than any of the ones around them.

c.  

```{r hsb2_hist2}
hist(hsb2$science, xlab="Science Scores", main="Distribution of Science Scores",freq=FALSE ) 
```

d.  

e.  

```{r hsb2_hist3}
hist(hsb2$math, xlab="Math Scores", main="Distribution of Math Scores" ) 
```

f.  The x value represents a score in math, the height represents the number of students which got that score.

g.  Although this plot still retains the triangle from the Science scores, there is a more even spread of scores between 40-60, rather than the two spikes from the Science score.

h.  

```{r hsb2_hist4}
hist(hsb2$math, xlab="Math Scores", main="Distribution of Math Scores", freq=FALSE ) 
```

## Activity 1.3.3

```{r hsb2_bar1}
counts = table(hsb2$race)
barplot(counts, main="Racial Demographics",xlab="Race") 
```

a.  Each bar represents a racial group, the height represents the number of students of said group.

b.  

c.  

```{r hsb2_bar2}
counts = table(hsb2$prog)
barplot(counts, main="School Programs",xlab="Program")
```

d.  Most students are in academic programs.

e.  Each bar represents a program, the heights represent number of students are in each type of program.

## Activity 1.3.4

```{r hsb2_groupedbar1}
counts = table(hsb2$prog, hsb2$schtyp)
barplot(counts, main="Program Type vs",xlab="School Type", 
  legend = rownames(counts), beside=TRUE)
```

a.  Each bar represents a program, the heights represent the number of students in each program at a specific type of school

b.  The private schools are smaller, and have proportionally less students in vocational programs

c.  

d.  

```{r hsb2_groupedbar2}
counts = table(hsb2$gender, hsb2$schtyp)
barplot(counts, main="School type vs",xlab="Gender", 
  legend = rownames(counts), beside=TRUE) 
```

e.  There are more female students overall

f.  Each bar is a gender at a different type of school, the heights are the number of students.

## Activity 1.3.5

```{r hsbs2_mosaic1}
counts = table(hsb2$prog, hsb2$schtyp)
mosaicplot(counts)
```

a.  The area of each rectangle is the relative number of students in a program at one type of school compared to another type of school. The position is what type of program it is, and what type of school it is at.

b.  This graph visualizes the relative difference between program sizes at different school types.

c.  

d.  

```{r hsb2_mosaic2}
counts = table(hsb2$gender, hsb2$prog)
mosaicplot(counts) 
```

e.  The gender ratio across different programs is almost the same.

f.  The rectangles represent the proportion of each gender that goes to each type of school.
