---
title: "DExam"
author: "Jeremiah Theisen"
date: "2024-10-08"
output: pdf_document
---

## D1 
1. 
a. 
```{r}
pnorm(1.3, mean=0, sd=1)
```
b.  
```{r} 
pnorm(-0.7, mean=0, sd=1)
```
c. 
0.903 - 0.242 = 0.661

d.
1 - 0.903 = 0.097

e.
```{r}
qnorm(0.28, mean=0, sd=1)
``` 
f. 1 - 0.15 = 0.85 

g.
```{r}
qnorm(0.15, mean=0, sd=1)
``` 
h. 0.09 for both 

i. 
```{r}
qnorm(0.09, mean=0, sd=1)
``` 
## D2 
2. 
a. 43 homeruns above 
b. 5.375 standard deviations 
c. z-score = (x - mean) / standard deviation 
z = 5.375  
```{r}
pnorm(5.375, mean=0, sd=1) 
pnorm(58, mean=15, sd=8) 
```

3. 
a. 
```{r}
pnorm(20, mean=15, sd=8)
``` 
1 - 0.734 = 0.266 

b. 
```{r} 
qnorm(0.90, mean=15, sd=8)
``` 
c.
```{r}
pnorm(20, mean=15, sd=8)
pnorm(25, mean=15, sd=8)
``` 
0.16 

d.
```{r}
qnorm(0.05, mean=15, sd=8)
qnorm(0.95, mean=15, sd=8)
``` 
k = 13.1588 

## D3 
4. 
a. Assuming that you are picking a shirt for each day, so order matters, P(12, 7) = 12!/5! = 3991680 
b. When buying ice cream, the order does not matter C(15, 4) = 1365 
c. Order does not matter for when a card is in your hand C(52, 2) = 1326 
d. Since there are 10 different people, order matters, since it determines who gets which card, so P(52, 10) = 5.7407 * 10^16 

## D4 
5. 
a. 0.32
b.
```{r}
numbaskets = rep(0, 1000)

 

freethrows=2

p=0.8

 

for(i in 1:freethrows){

  numbaskets=numbaskets+sample(c(1, 0), 1000, replace = TRUE, prob = c(p, 1-p))

}

hist(numbaskets)

print(freethrows)
```
c. 
```{r}
length(which(numbaskets==1))
``` 
This is very close to what I calculated 

## D5 
6. 
a. E(X) = np 
b. Var(X) = np(p-1) 

7. Binomial distributions and Normal distributions appear very similar, they are not directly related but sometimes can be used to approximate the other.
