---
title: "P1"
author: "Jeremiah Theisen"
date: "2024-09-10"
output: pdf_document
---
```{r}
loans = read.csv("https://github.com/TienChih/tbil-stats/raw/main/data/loans_full_schema.csv")

names(loans) 
```

## 2.1.1

a.  1/6
b.  2/6 =\> 1/3
c.  6/6 =\> 1/1
d.  5/6

## 2.1.2

a.  

```{r}
n=10                #number of die rolls

sixes=0             # of sixes rolled so far
Sixvec=rep(NA, n) #proportion of sixes rolled

for (i in 1:n){
  roll=sample(1:6,1,replace=TRUE)
  if (roll==6){
    sixes=sixes+1   #increment number of sixes
  }
  Sixvec[i]=sixes/i #records proportion of sixes so far
}

plot(Sixvec, type="l", ylim=c(0,1)) #plots linegraph of proportion of sixes
abline(h=1/6, col="red", lty=2)     #draw y=1/6 line
```

b. The number of 6s changes drastically each time the dice are rolled.

c.  

```{r}
n=100               #number of die rolls

sixes=0             # of sixes rolled so far
Sixvec=rep(NA, n) #proportion of sixes rolled

for (i in 1:n){
  roll=sample(1:6,1,replace=TRUE)
  if (roll==6){
    sixes=sixes+1   #increment number of sixes
  }
  Sixvec[i]=sixes/i #records proportion of sixes so far
}

plot(Sixvec, type="l", ylim=c(0,1)) #plots linegraph of proportion of sixes
abline(h=1/6, col="red", lty=2)     #draw y=1/6 line
```

d.  

```{r}
n=1000               #number of die rolls

sixes=0             # of sixes rolled so far
Sixvec=rep(NA, n) #proportion of sixes rolled

for (i in 1:n){
  roll=sample(1:6,1,replace=TRUE)
  if (roll==6){
    sixes=sixes+1   #increment number of sixes
  }
  Sixvec[i]=sixes/i #records proportion of sixes so far
}

plot(Sixvec, type="l", ylim=c(0,1)) #plots linegraph of proportion of sixes
abline(h=1/6, col="red", lty=2)     #draw y=1/6 line
```

e.  

```{r}
n=10000               #number of die rolls

sixes=0             # of sixes rolled so far
Sixvec=rep(NA, n) #proportion of sixes rolled

for (i in 1:n){
  roll=sample(1:6,1,replace=TRUE)
  if (roll==6){
    sixes=sixes+1   #increment number of sixes
  }
  Sixvec[i]=sixes/i #records proportion of sixes so far
}

plot(Sixvec, type="l", ylim=c(0,1)) #plots linegraph of proportion of sixes
abline(h=1/6, col="red", lty=2)     #draw y=1/6 line
```

f. The more times the dice is rolled, the number of 6s rolled approaches the expected value.

## 2.1.3

a.  A {6, 7, 8, 9, 10}
b.  B {2, 3, 5, 7}
c.  A number is chosen which is greater than 5 which is prime
d.  {7}
e.  A number is either greater than 5 or prime
f.  {2, 3, 5, 6, 8, 9, 10}
g.  Any number that is not prime
h.  {1, 4, 6, 8, 9, 10}
i.  A number which is not greater than 5 and prime
j.  {2, 3, 5}

## 2.1.4

a.  The event will never happen, and X = 0, or S = infinity Side note: For continuous numbers, the probability of any one number 0.

b.  The event will always happen, Y = S

c.  P(Z) \< 0 and P(Z) \> 1 cannot happen because A is a subset of S, or is equal to S. Also, a set cannot have a negative cardinality.

## 2.1.5
a. 5/10 => 1/2
b. 4/10 => 2/5
c. 1/10
(A and B) = {7}

d. 8/10 
(A or B) => {2, 3, 5, 7, 6, 8, 9, 10}

e. P(A or B) < P(A) < P(B) < P(A and B) 
f. SKIP - Done in class
g. P(A) + P(B) = 9/10, it is off by 1/10, which is P(A and B)
h. P(A) = 5/10, P(Ac) = 5/10 
P(B) = 4/10, P(Bc) = 6/10. The probability of a set and its complement should add up to the total sample size.

## 2.1.6 
a. 
```{r} 
length(which(loans$application_type=="joint"))
```
b. 
```{r} 
length(which(loans$homeownership=="MORTGAGE"))
```
c.
```{r} 
length(which(loans$application_type=="joint" & loans$homeownership=="MORTGAGE"))
```
d. P(J) = 0.1495 P(M) = 0.4795 P(M and J) = 0.095
P(M or J) = P(M) + P(J) - P(M and J) = 0.534

e.
```{r} 
index = sample(1:nrow(loans), 1000)
samp=loans[index,]

names(samp)
```

f.
```{r} 
table(samp$application_type,samp$homeownership)
``` 
             MORTGAGE OWN RENT
  individual      365 117  386
  joint            76  19   37 
  
g. 
P(J) = 0.132, P(H) = 0.136 P(J and H) = 0.019. P(M) = 0.441. 
The proportion of Mortage havers and Joint loans are very similar to the number calculated in d.


## 2.1.7 
a.
b.
```{r}
length(which(loans$state=="MS"))
```
c. 
```{r} 
length(which(loans$state=="MS" & loans$issue_month=="Jan-2018"))
```
d. 
```{r} 
index = sample(1:nrow(loans), 1000)
samp=loans[index,]

table(samp$state,samp$issue_month)
```
e. MS = 0.006 in sample, 0.0072 in loans. There are 0 loans from MS in Jan-2018 in sample, and 29 in the loans file. The probability for that in the file was 0.0029, which was really low, so it makes sense that in a random sample that never came up.