---
title: "P3"
author: "Jeremiah Theisen"
date: "2024-09-14"
output: pdf_document
---
```{r}
smallpox = read.csv("https://github.com/TienChih/tbil-stats/raw/main/data/smallpox.csv")

names(smallpox) 
```

## 2.3.1  
a. (C) = 70
b. (S|C) = 56
c. (!S|C) = 14
d. (!C) = 30
e. (S|!C) = 12
f. (!S|!C) = 18
g. Venn Diagram 
h. (S) = 68
i. P(S) = 0.68
j. P(C|S) = 0.824
k. P(!C|!S) = 0.5625

## 2.3.2
a. 
```{r}
cream = sample(c("cream", "no cream"), 100, replace = TRUE, prob = c(0.7, 0.3))
```
b. 
```{r} 
sugar = rep(NA, 100)

for(i in 1:100){
  if(cream[i]=="cream"){
    sugar[i]=sample(c("sugar", "no sugar"), 1, replace = TRUE, prob = c(0.8, 0.2))
  }
  else{
    sugar[i]=sample(c("sugar", "no sugar"), 1, replace = TRUE, prob = c(0.4, 0.6))
  }
}

sugar
```
c. 
```{r}
table(cream,sugar)
```

d. The values are off, but close enough given the sample size.

## 2.3.3  
a. P(S) = 68, this is the same value calculated earlier
b. P(S) = 0.48
c. P(S) = 0.6
d. P(S)  = 0.4
e. P(S) = 0.8
f. The visuals tell me that as P(C) goes up, so does P(S), as P(S|C) is higher than P(S|!C). The values of X line up well.

## 2.3.4  
a. P(Z|S)
b. P(Z|!S)
c. P(Z)
d. SKIP
e. SKIP


## 2.3.5 
a. p(innoculated) = 0.0392
```{r}
length(which(smallpox$inoculated=="yes"))
```
b. P(N) = 0.96
```{r}
inocpatients=subset(smallpox, smallpox$inoculated=="yes")
notinocpatients=subset(smallpox, smallpox$inoculated=="no")
nrow(notinocpatients)
```
c. P(D|I) = 0.024
```{r}
length(which(inocpatients$result=="died"))
```
d. P(D|N) = 0.1411
```{r}
length(which(notinocpatients$result=="died"))
```
e. P(I|D) = 6.898 * 10^-3, 0.0007
f. 
```{r}
diedpatients=subset(smallpox, smallpox$result=="died")
nrow(diedpatients)
```
g. 
```{r}
length(which(diedpatients$inoculated=="yes"))
``` 

P(I|D) = 7.06 * 10^-3; 0.0007. This is the same as was calculated earlier when simplified. Given how many decimal places were involved with the earlier equation, I would say that this is close enough. I did the calculation for e twice and got a similar number both times.