---
title: "P4"
author: "Jeremiah Theisen"
date: "2024-09-17"
output: pdf_document
---
## 2.4.1
a. 105
b. $11785
c. $117.85 

## 2.4.2 
a. P(X = 0) = 20
b. P(X = 137) = 55
c. P(X = 170) = 25
d. E(X) = 117.85, which is the same as the answer in c.
e. 
```{r}
textbookpurchases = sample(c(0, 137, 170), 100, replace = TRUE, prob = c(0.2, 0.55, 0.25))
hist(textbookpurchases)
```
f. This number is off by 10. This is off from what I expected by a bit.
107.65
```{r}
mean(textbookpurchases)
```
g. The mean was off by 1. This is closer to what we calculated
118.4781
```{r}
textbookpurchases = sample(c(0, 137, 170), 10000, replace = TRUE, prob = c(0.2, 0.55, 0.25))
hist(textbookpurchases)
mean(textbookpurchases)
```

## 2.4.3 
a. mean = 3.5. E(X) = 3.5, variance =  2.917 
b. 
```{r}
dierolls = sample(c(1, 2, 3, 4, 5, 6), 1000, replace = TRUE, prob = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
hist(dierolls)
```
c. 
It is close but off by a bit.
```{r}
mean(dierolls)
var(dierolls)
```


## 2.4.4 
a. The E(X) is similar to the mean. The main difference in how they are calculated is that the expected outcome takes probability into account, and is a bit more complcated. I believe that means that the expected value would be less skewed by large outliers.
b. They are similar because they both measure variation, just different types. They both have a number squared in them.

## 2.4.5 
a. Everything is 1/6th
b. E(x) = 3.5 
c. Var(X) = 2.914 
d. These are close to the numbers in the other exercises, the variance can be explained by human error for a and b and random error for a, along with using a different formula.

## 2.4.6 SKIP

## 2.4.7 
a. Xi = -2, 3, 98, 9998
b. P(X = -2) = .7989, P(X = 3) = 0.2, P(X = 98) = 0.001, P(X = 9998) = 0.00001
c. E(X) = -0.79982, Var(X) = 1016.117
d. They make money 
e.  
```{r}
ticketwinnings = sample(c(-2, 3, 98, 9998), 1000000, replace = TRUE, prob = c(0.7989, 0.2, 0.001, 0.0001))
hist(ticketwinnings)
```
f. 
mean: 0.06654
var: 9710.456
```{r}
mean(ticketwinnings) 
var(ticketwinnings) 
```