---
title: "PTest"
author: "Jeremiah Theisen"
date: "2024-09-24"
output: pdf_document
---

```{r}
quakes 
names(quakes)
```
## P1 
1.
a.
```{r}
length(which(quakes$mag==4.1))
length(which(quakes$mag==4.2))
``` 
b. 
P(4.1) = 55/800 = 0.06875
P(4.2) = 90/800 = 0.1125
c. 
``` {r}
index = sample(1:nrow(quakes), 100)

samp=quakes[index,]

 
table(samp$mag)
```

d. 
P(4.1|S) = 3/100 = 0.03
P(4.2|S) = 6/100 = 0.06 
The sample probabilities for 4.1 and 4.2 are both lower than for the entire population. 

## P2 
2.
a. P(C) = 13/52 => 1/4 => 0.25 
b. P(F10) = 16/52 => 4/13 => 0.3077 
c. P(C and F10) => 4/52 => 1/13 => 0.0769 
d. Independent because 
P(F10|C) = 0.0769/0.25 = 0.3077 = P(F10) 
P(C and F10) = 0.0769 = (0.25)(0.3077) = P(C)P(B)  
e. If you drew a card, and the first card was a club, the chance of drawing a club would be 12/51. This is dependent on the first event, since if the first card drawn was not a club, the chance of the second card being a club would be 13/51 which is not the same as 12/51. 

## P3 
3. P(B) = 2.75? 
(I know this is impossible, but I ran the algebra multiple times and this is what I got)

## P4 
4. 
a. 
-5, 3, 45, 9995 
b. E(X) = -1.14 
c. 
```{r}
ticketwinnings = sample(c(-5, 3, 45, 9995), 1000000, replace = TRUE, prob = c(0.73999, 0.22, 0.04, 0.00001))

hist(ticketwinnings)
```
d.
```{r}
mean(ticketwinnings)
```
This is off from my calculation by 0.071, which is not a lot. 

## P5 
5. E(Z) = 1.51
