---
title: "R1"
author: "Jeremiah Theisen"
date: "2024-09-14"
output: pdf_document
---

## 7.1.1
```{r}
possum = read.csv("https://github.com/TienChih/tbil-stats/raw/main/data/possum.csv")

names(possum)
``` 

a.
```{r}
plot(possum$skull_w, possum$head_l, pch=19)
```
b.The 62mm skull would be predicted to have a longer head 

c.53mm skull would be around 87mm long. 62mm skull would be around 96mm long. I would feel fairly confident that they would line up that way, but the exact numbers would be off by a bit.  

d.55mm. Very confident because there seems to be a large cluster at 55mm. 

## 7.1.2 
a. c and f have strong linear relationships. 

## 7.1.3
a. R = 0.35
b. R = -0.97
c. R = 0 
d. R = 0.65
e. R = -0.38
f. R = -0.85
g. R = 0.99
h. the same graph as f. 
i. R = 0.85

## 7.1.4
I would say (b) is the best fit 

## 7.1.5 
a. 
https://www.desmos.com/calculator/lbg4ya4vwx

b. It fits a lot better than it did before. 

## 7.1.6 
a. 
https://www.desmos.com/calculator/iyp0a1qf4e 
This B_0 is smaller, and the B_1 is larger

b. r = 0.8906. There is a strong but not perfect relationship. 

c. r^2 = 0.7931. There is a strong but not perfect relationship. 

d. 
```{r}
x1=c(1,2,3,4,4,5,6)
y1=c(1,3,2,4,5,4,7)

dummydata = data.frame(x1, y1)
```
e. 
```{r} 
dummymod=lm(y1~x1, data=dummydata) 
print(dummymod)
``` 
The slope and intercept are the same. 

f.
```{r}
cor(dummydata$x1, dummydata$y1)
``` 
g. 
```{r}
plot(dummydata$x1, dummydata$y1,  pch=19)
abline(dummymod, col="red")
```

## 7.1.7
a. 
```{r}
possummod=lm(head_l~skull_w, data=possum)
print(possummod)
``` 
The slope is 0.8158, and intercept is 46.1954
b. 
```{r}
cor(possum$skull_w, possum$head_l)
``` 

c. r = 0.710, r^2 = 0.5041. There is a weak correlation
d.
```{r}
plot(possum$skull_w, possum$head_l,  pch=19)
abline(possummod, col="red")
```
e. 
```{r}
summary(possummod)
```
f. 
```{r}
summary(possum)
```
g.
```{r}
possummod2=lm(total_l~tail_l, data=possum)
print(possummod2) 
summary(possummod2)
cor(possum$total_l, possum$tail_l)
plot(possum$total_l, possum$tail_l,  pch=19)
abline(possummod2, col="red")
```
```{r}
possummod3=lm(age~tail_l, data=possum)
print(possummod3) 
summary(possummod3)
cor(possum$age, possum$tail_l)
plot(possum$age, possum$tail_l,  pch=19)
abline(possummod3, col="red")
```


