---
title: "R2"
author: "Jeremiah Theisen"
date: "2024-10-15"
output: pdf_document
---

## 7.2.1 
```{r}
possum = read.csv("https://github.com/TienChih/tbil-stats/raw/main/data/possum.csv")
possummod=lm(head_l~skull_w, data=possum)
print(possummod)
print(cor(possum$skull_w, possum$head_l))
plot(possum$skull_w, possum$head_l,  pch=19)
abline(possummod, col="red")
``` 
a. Moderate 
b. 71% 
c. 89.3441 
d. 96.78 
e. 56.15 
f. mm/cm 
g. 0.8158 

## 7.2.2 
a.
b. R2 = 0.5448, R = -0.7381, there is a weak negative relationship
c. 54% 
d. The regression line measures age/price of the cars 
e. The slope represents how much more or less the car would cost as the car ages 
f. $5149 
g. 6.34 years old 

## 7.2.3
```{r}
mtl = read.csv("https://github.com/TienChih/tbil-stats/raw/main/data/mtl.csv")

names(mtl)
```
a. 
```{r}
plot(mtl$sitting, mtl$total, pch=19)
```
b. 
```{r}
mtlmod=lm(total~sitting, data=mtl)
```
c. 
```{r}
cor(mtl$sitting, mtl$total)
```
d. 
```{r}
plot(mtl$sitting, mtl$total,  pch=19)
abline(mtlmod, col="red")
```
e.
```{r}
summary(mtlmod)
``` 
f. R = 0.4, weak relationship. 
g. 15% 
h. The relationship between MLT Thickness and hours sitting. 
i. How thick the MLT is from hours sitting. 
j. 2.425 
k. 7.22 

## 7.2.4
a. No, because those are not actually causally related
b. Both would sell better in the summer, which both are causally related 

## 7.2.5
a. 117.24 inches 
b. Because most people do not grow to be that tall, growth slows down after 12-16ish 

## 7.2.6
a. 
```{r}
n=10
X=runif(n, 0, 10)
Y=runif(n, 0, 10)
mod=lm(Y~X)
print(cor(X, Y))
plot(X, Y, pch=19)
abline(mod)
``` 
0.5 was the highest value I got. 

b. 
```{r}
n=2
X=runif(n, 0, 10)
Y=runif(n, 0, 10)
mod=lm(Y~X)
print(cor(X, Y))
plot(X, Y, pch=19)
abline(mod)
``` 
It is related by 1

